Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-04 testbed.tex

>>>>

\subsection{fabric}

% Exit chroot, umount, and write to memory card
\begin{lstlisting}[]
from fabric.api import run, env, task
# Python Fabric script to run commands on multiple hosts through ssh
#
# Run script as 'fab <task>', where <task> is one of the scripts functions
# marked as a tesk. The task marked as 'default' will be run if <task> is not
# specified

env.hosts = ['rasp00.domain.com','rasp01.domain.com','rasp02.domain.com']
env.user = 'root'
env.password = 'sdn'

@task
def install(program):
    """
    Install a program
    program: program name
    """
    result = run('apt-get install -y {}'.format(program), quiet=True)

@task
def open(program, args):
    """
    Open af program
    program: program name
    args: program arguments
    """
    # Set environment variable DISPLAY=:0 and run commands
    with shell_env(DISPLAY=':0'):
        # Wake monitor
        run('xset dpms force on', quiet=True)

        # Run program
        run('{}'.format(program, " ".join(args)), quit=True)

\end{lstlisting}
\FloatBarrier

execute a script function by calling "fab install:feh"
